Tempus: Probabilistic Network Latency Verifier

### 2023-01-25 paper/5_eval.tex
[Paper] Updated fat tree figures and analysis

\subsection{Experiment Setup}
We tested Tempus on 5 real-world WAN topologies from the Topology Zoo and 3 datacenter topologies 
(fat-tree, with various amount of pods).
%TODO: stats of the topologies

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{optimization}
    \caption{Amount of convolution (in log scale) depending on what optimization strategy is applied}
    \label{fig:opt}
\end{figure}

@@

>>>>

\subsection{Experiment Setup}

\input{graph/table_top}

We tested Tempus on 5 real-world WAN topologies from the Topology Zoo and 3 datacenter topologies 
(fat-tree, with various amount of pods).
%TODO: stats of the topologies

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{optimization}
    \caption{Amount of convolution (in log scale) depending on what optimization strategy is applied}
    \label{fig:opt}
\end{figure}
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{optimization_fattree}
    \caption{Amount of convolution (in log scale) depending on what optimization strategy is applied}
    \label{fig:opt_fat}
\end{figure}

@@

\input{graph/table_analysis}
